An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-22 VLDB2026/main.tex
Update main.tex

	\textit{Single-Thread Search.}  
	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods. Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency. But, UNG slightly underperforms on high-LID datasets such as GloVe. In contrast, CAPS performs better on high-LID datasets but is more sensitive to dataset characteristics. CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.

>>>>

	\textit{Single-Thread Search.}  
	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods. Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency. But, UNG slightly \sout{underperforms on high-LID datasets such as GloVe.} In contrast, CAPS performs better on high-LID datasets but is more sensitive to dataset characteristics. CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.
